---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# rportr

<!-- badges: start -->
<!-- badges: end -->

The goal of rportr is to streamline the building of parameterized reports, including setup, table generation, and handling complex project directories.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("beaulucas/rportr")
```
## Examples

### Reading in data

This is a basic example which shows you how to solve a common problem:

Say you have a `./data` directory in your project, full of a mix of text files and RDS files. How to read all of them at once and assign them descriptive names?

Let's create a directory to demonstrate it.

```{r include=TRUE, echo=TRUE, message=FALSE, warning=FALSE}
dir.create("./data")
write.csv(mtcars, "./data/mtcars.csv")
saveRDS(iris, "./data/iris.rds", compress = FALSE)
```

The directory above takes the following structure:

```{r, eval = FALSE}
-- data
---- mtcars.csv
---- iris.rds
```

Now we will use `read_directory` to read in the file and assign variable names based on the file name.

```{r example}
library(rportr)
read_directory("./data")
```

```{r cleanup, include=FALSE, echo=FALSE}


```

### Setting up a project directory



### Formatting data for `kable`
